A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-02 mt-marathon.2013/PBML_article.tex
single threaded build compiles & passes regression

% Packages
% ========
% In this place you can load required packages by the \usepackage commands.
% The following packages are loaded automatically by the class:
% euler    (for math fonts)
% graphicx (for inclusion of images)
% multicol (for multicolumn typesetting)
% natbib   (for bibliography citations)
% amssymb  (for various symbols)
% If XeLaTeX is used, fontspec and xltxtra are loaded as well.
\usepackage{algorithmic}

@@

\section{Hypothesis and Translation Rule Evaluation}
\subsection{Old Framework}
The range of feature functions were hardcoded when evaluating the scores of hypotheses and translation rules. Translation rules are evaluated according to Equation~\ref{eq:translation rule score}
\begin{equation}
  score = \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_i) + \sum_{l  \in L} (\lambda_l * score_i) + \lambda_{wp} * words
\label{eq:translation rule score}
\end{equation}
where $T$ is the set of translation models, and $L$ is the set of sequence models, $\lambda_{m,i}$ is the i'th weight for translation model $m$, $\lambda_l$ is the weight for language model $l$, $\lambda_{wp}$ is the word penalty weight.

Similarly, hypotheses are evaluated as follows, Equation~\ref{hypothesis rule score}:
\begin{equation}
 score =  \sum_{i \in T} (\lambda_i * score_i)
    + \sum_{i \in L} (\lambda_i * score_i)
    + \lambda_{wp} * words
    + \lambda_d * score_d
    + \sum_{i \in R}(\lambda_i * score_i)
    + score_{future}
\label{hypothesis rule score}
\end{equation}

where $\lambda_d$ and $score_d$ is the distortion weight and score respectively, $R$ is the set of lexicalized reordering models.

When adding a new feature function, it would not be included in the scoring of the translation rule and hypotheses until Equation (1) and (2) are update.

>>>>

% Packages
% ========
% In this place you can load required packages by the \usepackage commands.
% The following packages are loaded automatically by the class:
% euler    (for math fonts)
% graphicx (for inclusion of images)
% multicol (for multicolumn typesetting)
% natbib   (for bibliography citations)
% amssymb  (for various symbols)
% If XeLaTeX is used, fontspec and xltxtra are loaded as well.
\usepackage{algorithmic}
\usepackage{amsmath}

@@

\section{Hypothesis and Translation Rule Evaluation}
\subsection{Old Framework}
The range of feature functions were hardcoded when evaluating the scores of hypotheses and translation rules. Translation rules are evaluated according to Equation~\ref{eq:translation rule score}
\begin{equation}
  score = \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) + \sum_{l  \in L} (\lambda_l * score_i) + \lambda_{wp} * words
\label{eq:translation rule score}
\end{equation}
where $T$ is the set of translation models, and $L$ is the set of sequence models, $\lambda_{m,i}$ is the i'th weight for translation model $m$, $\lambda_l$ is the weight for language model $l$, $\lambda_{wp}$ is the word penalty weight.

Similarly, hypotheses are evaluated as follows, Equation~\ref{eq:hypothesis rule score}:
\begin{equation}
\begin{split}
 score & =  \sum_{m \in T} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) \\
    & + \sum_{l \in L} (\lambda_l * score_l) \\
    & + \lambda_{wp} * words \\
    & + \lambda_d * score_d \\
    & + \sum_{m \in R} \sum_{i \in m} (\lambda_{m,i} * score_{m,i}) %\\
%    & + score_{future} \\
\label{eq:hypothesis rule score}
\end{split}
\end{equation}
where $\lambda_d$ is the distortion weight, and $R$ is the set of lexicalized reordering models.
%, and $score_{future}$ is the estimate of the future score for the hypothesis.

When adding a new feature function, its scores would not be included in the translation rule or hypothesis scores until the implementation of Equation~\ref{eq:translation rule score} and Equation~\ref{eq:hypothesis rule score} are update.
